Exercising choice over feedback schedules during practice is not advantageous for motor learning

### 2022-08-22 docs/accepted/supplementary.Rmd

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
  #- \pagewiselinenumbers
  - \raggedbottom
  - \AtBeginDocument{\let\maketitle\relax}
  - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
  - \renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
---

@@

\textcolor{blue}{We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not. Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment. None of the main effect or interactions were significant in Experiment 1 or Experiment 2. A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation} [@guadagnoli2001]\textcolor{blue}{. Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation} [e.g., @chiviacowsky2005]. \textcolor{blue}{Given recent support for this idea} [@bacelar2022]\textcolor{blue}{, it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.}

@@

\textcolor{blue}{Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity. Equivalence tests can be used to null findings more informative} [@harms2018; @lakens2017; @schuirmann1987]\textcolor{blue}{; however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons. First, we did not specify an \emph{a priori} smallest effect size of interest for any of the psychological constructs. Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol. Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points. We instead report mean differences and 90\% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments. The present experiments can be considered inconsistent with all effects larger than $g = \pm$ the largest absolute confidence interval bound presented in} Table \@ref(tab:tableS1).

>>>>

header-includes   :
  #- \usepackage{pdflscape}
  - \usepackage{setspace}
  #- \pagewiselinenumbers
  - \raggedbottom
  - \AtBeginDocument{\let\maketitle\relax}
  - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
  - \renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
---

@@

We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not. Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment. None of the main effect or interactions were significant in Experiment 1 or Experiment 2. A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation [@guadagnoli2001]. Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation [e.g., @chiviacowsky2005]. Given recent support for this idea [@bacelar2022], it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.

@@

Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity. Equivalence tests can be used to null findings more informative [@harms2018; @lakens2017; @schuirmann1987]; however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons. First, we did not specify an *a priori* smallest effect size of interest for any of the psychological constructs. Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol. Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points. We instead report mean differences and 90% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments. The present experiments can be considered inconsistent with all effects larger than $g = \pm$ the largest absolute confidence interval bound presented in Table \@ref(tab:tableS1).

### 2022-08-22 docs/preprint/preprint.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{setspace}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exercising choice over feedback schedules during practice is not advantageous for motor learning},
  pdflang={en-EN},
  pdfkeywords={Self-controlled, Knowledge of results, OPTIMAL theory, Retention},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\label{tab:table1}Cronbach's alpha for each questionnaire at each timepoint.}
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
\toprule
Questionnaire & After pre-test & After block 1 & After block 6 & Before retention\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 1}}\\
\hspace{1em}Perceived autonomy & 0.68 & 0.81 & 0.80 & 0.83\\
\hspace{1em}Perceived competence & 0.86 & 0.93 & 0.95 & 0.94\\
\hspace{1em}Intrinsic motivation & 0.86 & 0.90 & 0.92 & 0.93\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 2}}\\
\hspace{1em}Perceived autonomy & 0.39 & 0.73 & 0.79 & 0.85\\
\hspace{1em}Perceived competence & 0.92 & 0.88 & 0.91 & 0.91\\
\hspace{1em}Intrinsic motivation & 0.91 & 0.91 & 0.93 & 0.94\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase.}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:table2}Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.}
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Spatial goal} & \multicolumn{2}{c}{Timing goal} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Group & Total & Min--Max & Total & Min--Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 1}}\\
\hspace{1em}Choice+Error-Feedback & 4 & 0--2 & 30 & 0--4\\
\hspace{1em}Choice+Graded-Feedback & 2 & 0--1 & 26 & 0--4\\
\hspace{1em}Yoked+Error-Feedback & 1 & 0--1 & 28 & 0--3\\
\hspace{1em}Yoked+Graded-Feedback & 3 & 0--1 & 33 & 0--3\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 2}}\\
\hspace{1em}Choice+Binary-Feedback & 2 & 0--1 & 14 & 0--3\\
\hspace{1em}Yoked+Binary-Feedback & 4 & 0--1 & 10 & 0--2\\
\bottomrule
\end{tabular}
\end{table}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  doc, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{setspace}
\usepackage{tcolorbox}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exercising choice over feedback schedules during practice is not advantageous for motor learning},
  pdflang={en-EN},
  pdfkeywords={Self-controlled, Knowledge of results, OPTIMAL theory, Retention},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\label{tab:table1}Cronbach's alpha for each questionnaire at each timepoint.}
\resizebox{\linewidth}{!}{
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
\toprule
Questionnaire & After pre-test & After block 1 & After block 6 & Before retention\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 1}}\\
\hspace{1em}Perceived autonomy & 0.68 & 0.81 & 0.80 & 0.83\\
\hspace{1em}Perceived competence & 0.86 & 0.93 & 0.95 & 0.94\\
\hspace{1em}Intrinsic motivation & 0.86 & 0.90 & 0.92 & 0.93\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 2}}\\
\hspace{1em}Perceived autonomy & 0.39 & 0.73 & 0.79 & 0.85\\
\hspace{1em}Perceived competence & 0.92 & 0.88 & 0.91 & 0.91\\
\hspace{1em}Intrinsic motivation & 0.91 & 0.91 & 0.93 & 0.94\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase.}\\
\end{tabular}}
\end{table}

@@

\caption{\label{tab:table2}Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.}
\resizebox{\linewidth}{!}{
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Spatial goal} & \multicolumn{2}{c}{Timing goal} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Group & Total & Min--Max & Total & Min--Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 1}}\\
\hspace{1em}Choice+Error-Feedback & 4 & 0--2 & 30 & 0--4\\
\hspace{1em}Choice+Graded-Feedback & 2 & 0--1 & 26 & 0--4\\
\hspace{1em}Yoked+Error-Feedback & 1 & 0--1 & 28 & 0--3\\
\hspace{1em}Yoked+Graded-Feedback & 3 & 0--1 & 33 & 0--3\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 2}}\\
\hspace{1em}Choice+Binary-Feedback & 2 & 0--1 & 14 & 0--3\\
\hspace{1em}Yoked+Binary-Feedback & 4 & 0--1 & 10 & 0--2\\
\bottomrule
\end{tabular}}
\end{table}
